Hydra Battles and Cie

### 2021-09-19 doc/part-hydras.tex
adapt hydras text about Comparable typeclass

\subsection{A class for ordinal notations}

@@

\subsubsection{The \texttt{Comparable class}}

The following class, contributed by Jérémy Damour and Théo Zimmermann, allows us to apply generic lemmas and tactics
about decidable strict orders.
The correctness of the comparison function is expressed through Stdlib's type 
\texttt{Datatypes.CompareSpec}.

\begin{Coqsrc}
Inductive CompareSpec (Peq Plt Pgt : Prop) : comparison -> Prop :=
    CompEq : Peq -> CompareSpec Peq Plt Pgt Eq
  | CompLt : Plt -> CompareSpec Peq Plt Pgt Lt
  | CompGt : Pgt -> CompareSpec Peq Plt Pgt Gt.
\end{Coqsrc}

>>>>

\subsection{Classes for ordinal notations}

@@

\subsubsection{The \texttt{Comparison} and \texttt{Comparable} classes}

We use the operational class \texttt{Comparison} of comparison functions to define the \texttt{Comparable} class, contributed by Jérémy Damour and Théo Zimmermann, which allows us to apply generic lemmas and tactics about decidable strict orders.
The correctness of the comparison function is expressed through Stdlib's type 
\texttt{Datatypes.CompareSpec} as specialized by \texttt{Datatypes.CompSpec}.

\begin{Coqsrc}
Inductive CompareSpec (Peq Plt Pgt : Prop) : comparison -> Prop :=
    CompEq : Peq -> CompareSpec Peq Plt Pgt Eq
  | CompLt : Plt -> CompareSpec Peq Plt Pgt Lt
  | CompGt : Pgt -> CompareSpec Peq Plt Pgt Gt.

Definition CompSpec {A} (eq lt : A->A->Prop)(x y:A) : comparison -> Prop :=
 CompareSpec (eq x y) (lt x y) (lt y x).
\end{Coqsrc}
